|

### 2022-12-21 paper_comparison/paper_comparison/paper_comparison.Rmd
Update Rorschach description

### Subject allocation

@@

As mentioned in Section \ref{calculating-p-values-for-the-visual-test}, $\alpha$ used in Equation \ref{eq:pvalue-beta-binomial} needs to be estimated using Rorschach lineups. Hence, 36 lineups with all combinations of $n$ and $X_{raw}$ and three replications were included in experiment III. In these lineups, the data of the data plot was generated from a model consistent with the null hypothesis, while the data of the 19 null plots were generated using the same simulation method discussed in Section \ref{sampling-from-the-null-distribution}. Technically, this was an alternative to Rorschach lineup but with the null distribution further conditioning on the estimated coefficients and the residual sum of squares. Thus, we used another valid method suggested in @vanderplas2021statistical which was designed for typical lineups to estimate $\alpha$. Considering the differnece between typical lineups and Rorschach lineups, we have also included a sensitivity analysis in the Appendix to examine the impact of the variance of the estimate on our findings.

>>>>

### Subject allocation
\newcommand{\svp}[1]{{\textcolor{RedOrange}{#1}}}

@@

As mentioned in Section \ref{calculating-p-values-for-the-visual-test}, $\alpha$ used in Equation \ref{eq:pvalue-beta-binomial} needs to be estimated using \svp{null} lineups. Hence, 36 lineups with all combinations of $n$ and $X_{raw}$ and three replications were included in experiment III. In these lineups, the data of the data plot was generated from a model \svp{with zero effect size}, while the data of the 19 null plots were generated using the same simulation method discussed in Section \ref{sampling-from-the-null-distribution}. \svp{This generation procedure differs from the canonical Rorschach lineup procedure, which requires that all 20 plots are generated from the null hypothesis. However, these lineups serve the same fundamental purpose: to assess the number of visually interesting plots generated under the null hypothesis.}
<!-- Technically, this was an alternative to Rorschach lineup but with the null distribution further conditioning on the estimated coefficients and the residual sum of squares.  -->
\svp{To account for the fact that our simulation method for these lineups is not the Rorschach procedure,} we used the method suggested in @vanderplas2021statistical for typical lineups containing a data plot to estimate $\alpha$. 
We have included a sensitivity analysis in the Appendix to examine the impact of the variance of the $\alpha$ estimate on our findings.
